---
title: "Untitled"
author: "Canberk Bulut"
date: "14 12 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Gerekli Kütüphaneler
```{r}
library("plotly")
library("readr")
library("readxl")
library("forecast")
library("tseries")
library("lmtest")
library("TTR") 
library("stats")
library("tidyverse")
library("ggplot2")
library("rugarch")
library("rmgarch")
library("MTS")
library("keras")
library("tensorflow")
library("Metrics")
library(e1071)
```



```{r}
setwd("C:/Users/cberk/Downloads")
nasdaq<-read_xlsx("nasdaq_closed2.xlsx")
dax<-read_xlsx("dax_closed2.xlsx")
```

```{r}
nasdaq2<-nasdaq[-1]
ts.nasdaq<-ts(nasdaq2,frequency = 365)
ts.plot(ts.nasdaq)
nasdaq3<-log(nasdaq2)
nasdaq4<-diff(nasdaq3$Close,differences = 1)
df<-data.frame(Close=nasdaq4)
date<-data.frame(nasdaq$Date[-1])
nasdaq5<-cbind(date,df)



```
logdiff olanlarına lstm ve arima uygula ,svm 
```{r}
fit=arima(ts.nasdaq,order=c(0,1,1))
r=resid(fit)
```

```{r}
archTest(r)
spec4=ugarchspec(variance.model=list(model="eGARCH", garchOrder=c(1,1)),

               mean.model=list(armaOrder=c(1,1), include.mean=TRUE),distribution.model="nig")

```

```{r}
def.fit=ugarchfit(spec=spec4,data=nasdaq4, solver='hybrid',distribution.model="nig")
print(def.fit)
```



```{r}
dax2<-dax[-1]
ts.dax<-ts(dax2,frequency = 365)
ts.plot(ts.dax)
dax3<-log(dax2)
dax4<-diff(dax3$Close,differences = 1)
df2<-data.frame(Close=dax4)
date2<-data.frame(dax$Date[-1])
dax5<-cbind(date2,df2)



```

```{r}
acf(ts.dax,lag.max = 50)
```

```{r}
pacf(ts.dax,lag.max = 50)
```
```{r}
ts.daxdiff<-diff(ts.dax,difference=1)
acf(ts.daxdiff,lag.max = 50)
```
  
  
  
```{r}
pacf(ts.daxdiff,lag.max = 50)


```
```{r}
ts.daxlogdiff<-diff(log(ts.dax),difference=1)
acf(ts.daxlogdiff,lag.max = 50)
```

```{r}
pacf(ts.daxlogdiff,lag.max=50)
```

#NASDAQ



```{r}
acf(ts.nasdaq,lag.max = 50)
```

```{r}
pacf(ts.nasdaq,lag.max = 50)
```

```{r}
ts.nasdaqdiff<-diff(ts.nasdaq,difference=1)
acf(ts.nasdaqdiff,lag.max = 50)
```
  
  
  
```{r}
pacf(ts.nasdaqdiff,lag.max = 50)


```

```{r}
ts.nasdaqlogdiff<-diff(log(ts.nasdaq),difference=1)
acf(ts.nasdaqlogdiff,lag.max = 50)
```

```{r}
ts.nasdaq5<-ts(nasdaq5$Close,frequency=365)
arima_012<-auto.arima(ts.nasdaqlogdiff)
```

```{r}
pacf(ts.nasdaqlogdiff,lag.max=50)
```





```{r}
dateID <- nasdaq5$Date[2:nrow(nasdaq5)]
supervised <- as.data.frame(cbind(lag(df,1), df))
supervised[is.na(supervised)] <- 0
n_ <- round(nrow(nasdaq5) * .70, digits = 0)
train <- supervised[1:n_, ]
test <- supervised[(n_+1):1206,]
train_id <- dateID[1:n_]
test_id <- dateID[(n_+1):1206]



```






```{r}
scale_data <- function(train, test, feature_range = c(0,1)) {
  x = train
  fr_min = feature_range[1]
  fr_max = feature_range[2]
  std_train = (x - min(x)) / (max(x) - min(x))
  std_test = (test - min(x)) / (max(x) - min(x))
  
  scaled_train = std_train * (fr_max - fr_min) + fr_min
  scaled_test = std_test * (fr_max - fr_min) + fr_min

  return( list(scaled_train = as.vector(scaled_train), scaled_test = as.vector(scaled_test) ,scaler= c(min =min(x), max = max(x))) )
}
```

```{r}
reverse_scaling <- function(scaled, scaler, feature_range = c(0,1)) {
  min = scaler[1]
  max = scaler[2]
  t = length(scaled)
  mins = feature_range[1]
  maxs = feature_range[2]
  inverted_dfs = numeric(t)
  
  for(i in 1:t) {
    X = (scaled[i] - mins) / (maxs - mins)
    rawValues = X * (max - min) + min
    inverted_dfs[i] <- rawValues
  }
  return(inverted_dfs)
}
```



```{r}
Scaled <- scale_data(train, test, c(-1,1))

x_train <- Scaled$scaled_train[,1]
y_train <- Scaled$scaled_train[,2]

x_test <- Scaled$scaled_test[,1]
y_test <- Scaled$scaled_test[,2]
```


```{r}
dim(x_train) <- c(length(x_train), 1,1)
X_shape2 <- dim(x_train)[2]
X_shape3 <- dim(x_train)[3]
batch_size <- 1
units <- 100
n_timesteps <- 12
n_predictions <- n_timesteps

build_matrix <- function(tseries, overall_timesteps) {
  t(sapply(1:(length(tseries) - overall_timesteps + 1), function(x) 
    tseries[x:(x + overall_timesteps - 1)]))
}
reshape_X_3d <- function(X) {
  dim(X) <- c(dim(X)[1], dim(X)[2], 1)
  X
}


```








```{r}
model.lstm <- keras_model_sequential()

```


```{r}

model.lstm %>% 
  layer_lstm(units, batch_input_shape = c(batch_size, X_shape2, X_shape3), stateful = TRUE) %>%
  layer_dense(units = 1)
```



```{r}
model.lstm %>% 
  compile(loss = 'mean_squared_error',
          optimizer = optimizer_adam(lr = 0.03, decay = 1e-6),
          metrics = c('accuracy','mse','mae'))
```

```{r}

  
history <- model.lstm %>% fit(x_train,y_train,
                              epochs = 25,
                              batch_size = 128,
                              validation_split = 0.2,
                              shuffle=FALSE)
```

```{r}
L = length(x_test)
scaler = Scaled$scaler
predictions = numeric(L)
Series=supervised[,1]

for(i in 1:L){
  X = x_test[i]
  dim(X) = c(1,1,1)
  yhat = model.lstm %>% predict(X, batch_size=batch_size)
  # invert scaling
  yhat = reverse_scaling(yhat, scaler,  c(-1, 1))
  # invert differencing
  yhat  = yhat + as.numeric(Series[(n_+i)])
  # store
  predictions[i] <- yhat
}
names(test)[1] <- "Closed"
lstmMAE<-mae(test$Close,predictions)
lstmMAPE<-mape(test$Close,predictions)
lstmMSE<-mse(test$Close,predictions)
lstmRMSE<-rmse(test$Close,predictions)
LSTMe<-cbind(lstmMAE,lstmMAPE,lstmMSE,lstmRMSE)


cbind(test$Closed,predictions)
e_lstm<-predictions-test$Closed
```
prediction ve actual olarak grafiklerini çizdiricek(tsplot).

#Nasdaq prediction plot
```{r}
ts.closed_nasdaq<-ts(test[2],frequency = 365)
deneme2<-ts(predictions,frequency = 365)
df3<-as.data.frame(cbind(deneme2,ts.closed_nasdaq))
satir2 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih2<- nasdaq5[(satir2+1):1206,]
df3%>%
  ggplot(aes(x=tarih2$nasdaq.Date..1.,y=deneme2))+
  geom_line(color="red")+
  geom_line(y=ts.closed_nasdaq,color="blue")
```

# GARCH NASDAQ

#GARCH

```{r}
a=ugarchspec(variance.model = 
               list(model="eGARCH",garchOrder=c(1,1)),mean.model=list(armaOrder=c(1,1)),distribution.model="nig")
a_fit=ugarchfit(spec=a,data=nasdaq5$Close)
```
nig, jsu
```{r}
a_fit
```


```{r}
b=ugarchspec(variance.model = 
               list(model="iGARCH",garchOrder=c(1,1)))
b_fit=ugarchfit(spec=b,data=nasdaq5$Close)
```

```{r}
b_fit
```





```{r}
garchfitted<-fitted(a_fit)
x<-as.data.frame(garchfitted)
row.names(x) <- NULL
x2<- cbind(x, nasdaq5$nasdaq.Date..1)
#garchfitted<-garchfitted[-2]
#garchfitted<-as.data.frame(cbind(garchfitted, as.data.frame(dax5$dax.Date..1.)))
#garchfitted <- garchfitted[-1,]
#garchfitted <- cbind(garchfitted, dax5[-1,])
x2$set <- "train"
x2$number<- 1:1206
nasdaq5$number<-1:1206
x2$set[x2$`number` > 844] <- "test"
x2$x2[x2$`number` > 844]<-nasdaq5$Close[nasdaq5$`number`>844]
#garchPlot <- plot_ly(garchfitted, x = ~`Date`) %>%
 # add_trace(y = ~Close, mode = "lines", name = "Interest Rate") %>%
  #add_trace(y = ~garchfitted, mode = "lines", name = "Interest Rate") %>%
  #layout(title = "GARCH")
garchMAE <- x2 %>% filter(set == "test") %>% select(`V1`, `x2`)
 garchMAE2 <- mae(garchMAE$`V1`, as.numeric(test[,2]))
 garchMAE2
 garchMAPE2 <- mape(garchMAE$`V1`, as.numeric(garchMAE$`x2`))
 garchMSE2 <- mse(garchMAE$`V1`, as.numeric(garchMAE$`x2`))
 garchRMSE2 <- rmse(garchMAE$`V1`, as.numeric(garchMAE$`x2`))
 GARCHe<-cbind(garchMAE2,garchMAPE2,garchMSE2,garchRMSE2)
 
 e_garch<-garchMAE$x2-garchMAE$V1
```

```{r}
#xy<-x2$set=="test"
ts.closed_nasdaq2<-ts(test[,2],frequency = 365)
deneme3<-ts(x2$V1[845:1206],frequency = 365)
df4<-as.data.frame(cbind(deneme3,ts.closed_nasdaq2))
satir3 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih3<- nasdaq5[(satir3+1):1206,]
df4%>%
  ggplot(aes(x=tarih3$nasdaq.Date..1.,y=deneme3))+
  geom_line(color="red")+
  geom_line(y=ts.closed_nasdaq2,color="blue")
  scale_y_continuous( limits=c(-0.2045, 0.2045))
```
#ARIMA PREDICTION
```{r}
tt<-rbind(train[2],test[2])
arima_012<-auto.arima(ts(tt,frequency = 365))
```


```{r}
arimaFit <- arima_012
arimaFitted <- arimaFit$fitted
arimaFitted <- as.data.frame(cbind(arimaFitted, nasdaq5$Date ))
arimaFitted <- cbind(arimaFitted, nasdaq5)
arimaFitted$set[arimaFitted$number > 844] <- "test2"
arimaFitted$set[arimaFitted$set == "train2"] <- NA
arimaMAE2 <- arimaFitted %>% filter(set == "test2") %>% select(`Close`, x)
 arimaMAE <- mae(arimaMAE2$`Close`, as.numeric(arimaMAE2$x))
 arimaMAE
 arimaMAPE <- mape(arimaMAE2$`Close`, as.numeric(arimaMAE2$x))
 arimaMSE <- mse(arimaMAE2$`Close`, as.numeric(arimaMAE2$x))
 arimaRMSE <- rmse(arimaMAE2$`Close`, as.numeric(arimaMAE2$x))
ARIMAe<-cbind(arimaMAE,arimaMAPE,arimaMSE,arimaRMSE)
 e_arima<-arimaMAE2$x-arimaMAE2$Close
```


# SVM NASDAQ


#SVM MODEL
```{r}

daily_data <- nasdaq5[2][-1206,]
days <- 1:1206
x<- nasdaq5[-1,]
DF <- data.frame(x,daily_data)
DF<-DF[-1]
DF<-DF[-2]
colnames(DF)<-c("y","x")


# train an svm model, consider further tuning parameters for lower MSE
svmodel <- svm(y ~ x,data=DF, type="eps-regression",kernel="radial",cost=10000, gamma=10)
#specify timesteps for forecast, eg for all series + 12 months ahead
nd <- 1:1206
#compute forecast for all the 156 months 
prognoza <- predict(svmodel, newdata=data.frame(x=nasdaq5$Close))


```

```{r}

svmFitted <- prognoza
svmFitted <- as.data.frame(cbind(svmFitted, nasdaq5$nasdaq.Date..1 ))
svmFitted <- cbind(svmFitted, nasdaq5)
#svmFitted$set <- "train2"
svmFitted$set[svmFitted$`number` > 844] <- "test2"
svmFitted$svmFitted[svmFitted$set == "train2"] <- NA
#svmPlot <- plot_ly(arimaFitted, x = ~`Date`) %>%
 # add_trace(y = ~Close, mode = "lines", name = "Interest Rate") %>%
  #add_trace(y = ~arimaFitted, mode = "lines", name = "Interest Rate") %>%
  #layout(title = "ARIMA")
pred <- svmFitted %>% filter(set == "test2") %>% select(`Close`, svmFitted)
 svmMAE <- mae(pred$`Close`, as.numeric(pred$svmFitted))
 svmMAE
 svmMAPE<-mape(pred$`Close`, as.numeric(pred$svmFitted))
 svmMSE<-mse(pred$`Close`, as.numeric(pred$svmFitted))
 svmRMSE<-rmse(pred$`Close`, as.numeric(pred$svmFitted))
 pred
  e_svm<-pred$svmFitted-pred$Close
  SVMe<-cbind(svmMAE,svmMAPE,svmMSE,svmRMSE)

```




```{r}
ts.closed_nasdaq3<-ts(test[2],frequency=365)
deneme4<-ts(svmFitted$svmFitted[845:1206],frequency = 365)
df5<-as.data.frame(cbind(deneme4,ts.closed_nasdaq3))
satir4 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih4<- nasdaq5[(satir4+1):1206,]
df5%>%
  ggplot(aes(x=tarih4$nasdaq.Date..1.,y=deneme4))+
  geom_line(color="red")+
  geom_line(y=ts.closed_nasdaq3,color="blue")+
  scale_y_continuous( limits=c(-0.025, 0.025))
  
```

# SVM 2 FARK ALINMIS
```{r}

daily_data <- nasdaq5[2][-1206,]
daily_data<-daily_data[1:1204]
days <- 1:1204
x<- nasdaq5[-2,]
x<-x[-1,]
DF <- data.frame(x,daily_data)
DF<-DF[-1]
DF<-DF[-2]
colnames(DF)<-c("y","x")


# train an svm model, consider further tuning parameters for lower MSE
svmodel <- svm(y ~ x,data=DF, type="eps-regression",kernel="radial",cost=10000, gamma=10)
#specify timesteps for forecast, eg for all series + 12 months ahead
nd <- 1:1204
#compute forecast for all the 156 months 
prognoza <- predict(svmodel, newdata=data.frame(x=nasdaq5$Close))



```






# GARCH_SVM HYBRID

```{r}
garchfitted<-fitted(a_fit)
x<-as.data.frame(garchfitted)
x <- x[order(-x$V1),, drop=FALSE];row.names(x) <- NULL
x2<- cbind(x, nasdaq5$nasdaq.Date..1)

x2$set <- "train"
x2$number<- 1:1206
nasdaq5$number<-1:1206
x2$set[x2$`number` > 844] <- "test"
x2$x2[x2$`number` > 844]<-nasdaq5$Close[nasdaq5$`number`>844]

garchMAE <- x2 %>% filter(set == "test") %>% select(`V1`, `x2`)
 garchMAE2 <- mae(garchMAE$`V1`, as.numeric(garchMAE$`x2`))
 garchMAE2
 e_garch<-garchMAE$x2-garchMAE$V1
x3<-as.data.frame(cbind(x2$V1[845:1206],x2$number[845:1206]))
x4<-as.data.frame(cbind(x2$V1[845:1206],x2$number[845:1206]))
x4<-x4[-845,]
x3<-x3[-1,]
svm_garch_tune<-tune.svm(
     test[,2]~ e_garch,
	    data = test,
	    gamma = 2 ^ (-1:1),
	    cost = 2 ^ (2:8), 
	    epsilon = seq(0, 1, 0.1),
	    kernel = "radial"
	)
	svm_garch <- svm_garch_tune$best.model
svm_garch_pred <- fitted(svm_garch)
```

```{r}
hybrid_svmgarch_pred<-svm_garch_pred+pred$svmFitted

a<-test
hybrid_svmgarch_pred_mae<-mae(hybrid_svmgarch_pred, a[,2])
hybrid_svmgarch_pred_mse<-mse(hybrid_svmgarch_pred, a[,2])
hybrid_svmgarch_pred_rmse<-rmse(hybrid_svmgarch_pred, a[,2])
hybrid_svmgarch_pred_mape<-mape(hybrid_svmgarch_pred, a[,2])
GARCH_SVM<-cbind(hybrid_svmgarch_pred_mae,hybrid_svmgarch_pred_mape,hybrid_svmgarch_pred_mse,hybrid_svmgarch_pred_rmse)
```

```{r}
ts.closed_nasdaq4<-ts(test[,2],frequency=365)
deneme6<-ts(hybrid_svmgarch_pred,frequency = 365)
df6<-as.data.frame(cbind(deneme6,ts.closed_nasdaq4))
df6$actual <- "actual"
df6$prediction<-"prediction"
satir6 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih6<- nasdaq5[(satir6+1):1206,]
df6%>%
  ggplot(aes(x=tarih6$nasdaq.Date..1.,y=deneme6,group=prediction,color=prediction))+
  geom_line(aes(y=ts.closed_nasdaq4,group=actual,color=actual))+
  geom_line(aes(y=deneme6,group=prediction,color=prediction))+
labs(x = "Date", y = "NASDAQ Closed Value", color = "Data\n") +
  scale_color_manual(labels = c("Prediction", "Actual"), values = c("blue", "red")) 
  scale_y_continuous( limits=c(-0.025, 0.025))

```




#ARIMA_SVM HYBRID

```{r}
svm_arima_tune<-tune.svm(
     test[,2]~ e_arima,
	    data = test,
	    gamma = 2 ^ (-1:1),
	    cost = 2 ^ (2:8), 
	    epsilon = seq(0, 1, 0.1),
	    kernel = "radial"
	)
	svm_arima <- svm_arima_tune$best.model
svm_arima_pred <- fitted(svm_arima)
```



```{r}
hybrid_svmarima_pred<-svm_arima_pred+pred$svmFitted

a<-test
hybrid_svmarima_pred_mae<-mae(hybrid_svmarima_pred, a[,2])
hybrid_svmarima_pred_mse<-mse(hybrid_svmarima_pred, a[,2])
hybrid_svmarima_pred_rmse<-rmse(hybrid_svmarima_pred, a[,2])
hybrid_svmarima_pred_mape<-mape(hybrid_svmarima_pred, a[,2])
ARIMA_SVM<-cbind(hybrid_svmarima_pred_mae,hybrid_svmarima_pred_mape,hybrid_svmarima_pred_mse,hybrid_svmarima_pred_rmse)
```



```{r}
ts.closed_nasdaq5<-ts(test[,2],frequency=365)
deneme7<-ts(hybrid_svmarima_pred,frequency = 365)
df7<-as.data.frame(cbind(deneme7,ts.closed_nasdaq5))
df7$actual <- "actual"
df7$prediction<-"prediction"
satir7 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih7<- nasdaq5[(satir7+1):1206,]
df7%>%
  ggplot(aes(x=tarih7$nasdaq.Date..1.,y=deneme7,color=prediction))+
  geom_line(aes(y=ts.closed_nasdaq5,color=actual))+
  geom_line(aes(y=deneme7,color=prediction))+
labs(x = "Date", y = "NASDAQ Closed Value", color = "Data\n") +
  scale_color_manual(labels = c("Prediction", "Actual"), values = c("blue", "red"))  
  scale_y_continuous( limits=c(-0.025, 0.025))




```



#ARIMA_LSTM HYBRID

```{r}
dateID <- nasdaq5$Date[2:nrow(nasdaq5)]
supervised <- as.data.frame(cbind(lag(df,1), df))
supervised[is.na(supervised)] <- 0
n_ <- round(nrow(nasdaq5) * .70, digits = 0)
train <- supervised[1:n_, ]
test <- supervised[(n_+1):1206,]
train_id <- dateID[1:n_]
test_id <- dateID[(n_+1):1206]



```






```{r}
scale_data <- function(train, test, feature_range = c(0,1)) {
  x = train
  fr_min = feature_range[1]
  fr_max = feature_range[2]
  std_train = (x - min(x)) / (max(x) - min(x))
  std_test = (test - min(x)) / (max(x) - min(x))
  
  scaled_train = std_train * (fr_max - fr_min) + fr_min
  scaled_test = std_test * (fr_max - fr_min) + fr_min

  return( list(scaled_train = as.vector(scaled_train), scaled_test = as.vector(scaled_test) ,scaler= c(min =min(x), max = max(x))) )
}
```

```{r}
reverse_scaling <- function(scaled, scaler, feature_range = c(0,1)) {
  min = scaler[1]
  max = scaler[2]
  t = length(scaled)
  mins = feature_range[1]
  maxs = feature_range[2]
  inverted_dfs = numeric(t)
  
  for(i in 1:t) {
    X = (scaled[i] - mins) / (maxs - mins)
    rawValues = X * (max - min) + min
    inverted_dfs[i] <- rawValues
  }
  return(inverted_dfs)
}
```



```{r}
Scaled <- scale_data(train, test, c(-1,1))

x_train <- Scaled$scaled_train[,1]
y_train <- Scaled$scaled_train[,2]

x_test <- Scaled$scaled_test[,1]
y_test <- Scaled$scaled_test[,2]
```


```{r}
dim(x_train) <- c(length(x_train), 1,1)
X_shape2 <- dim(x_train)[2]
X_shape3 <- dim(x_train)[3]
batch_size <- 1
units <- 100
n_timesteps <- 12
n_predictions <- n_timesteps

build_matrix <- function(tseries, overall_timesteps) {
  t(sapply(1:(length(tseries) - overall_timesteps + 1), function(x) 
    tseries[x:(x + overall_timesteps - 1)]))
}
reshape_X_3d <- function(X) {
  dim(X) <- c(dim(X)[1], dim(X)[2], 1)
  X
}


```








```{r}
model.lstm <- keras_model_sequential()

```


```{r}

model.lstm %>% 
  layer_lstm(units, batch_input_shape = c(batch_size, X_shape2, X_shape3), stateful = TRUE) %>%
  layer_dense(units = 1)
```



```{r}
model.lstm %>% 
  compile(loss = 'mean_squared_error',
          optimizer = optimizer_adam(lr = 0.03, decay = 1e-6),
          metrics = c('accuracy','mse','mae'))
```

```{r}

  
history <- model.lstm %>% fit(x_train,y_train,
                              epochs = 25,
                              batch_size = 128,
                              validation_split = 0.2,
                              shuffle=FALSE)
```

```{r}
L = length(e_arima)
scaler = Scaled$scaler
predictions2 = numeric(L)
Series=supervised[,1]

for(i in 1:L){
  X = e_arima[i]
  dim(X) = c(1,1,1)
  yhat = model.lstm %>% predict(X, batch_size=batch_size)
  # invert scaling
  yhat = reverse_scaling(yhat, scaler,  c(-1, 1))
  # invert differencing
  yhat  = yhat + as.numeric(Series[(n_+i)])
  # store
  predictions2[i] <- yhat
}
predictions2
```




```{r}
hybrid_arimalstm_pred<-predictions2+ arimaMAE2$x

a<-test
hybrid_arimalstm_pred_mae<-mae(hybrid_arimalstm_pred, a[,2])
hybrid_arimalstm_pred_mse<-mse(hybrid_arimalstm_pred, a[,2])
hybrid_arimalstm_pred_rmse<-rmse(hybrid_arimalstm_pred, a[,2])
hybrid_arimalstm_pred_mape<-mape(hybrid_arimalstm_pred, a[,2])
ARIMA_LSTM<-cbind(hybrid_arimalstm_pred_mae, hybrid_arimalstm_pred_mape, hybrid_arimalstm_pred_mse, hybrid_arimalstm_pred_rmse)

```






```{r}
ts.closed_nasdaq5<-ts(test[,2],frequency=365)
deneme8<-ts(hybrid_arimalstm_pred,frequency = 365)
df8<-as.data.frame(cbind(deneme8,ts.closed_nasdaq5))
df8$actual <- "actual"
df8$prediction<-"prediction"
satir8 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih8<- nasdaq5[(satir7+1):1206,]
df8%>%
  ggplot(aes(x=tarih8$nasdaq.Date..1.,y=deneme8,group=prediction,color=prediction))+
  geom_line(aes(y=ts.closed_nasdaq5,group=actual,color=actual))+
  geom_line(aes(y=deneme8,group=prediction,color=prediction))+
  labs(x = "Date", y = "NASDAQ Closed Value", color = "Data\n") +
  scale_color_manual(labels = c("Prediction", "Actual"), values = c("blue", "red")) 
  scale_y_continuous( limits=c(-0.025, 0.025))

```

# GARCH-LSTM HYBRID

```{r}
L = length(e_garch)
scaler = Scaled$scaler
predictions3 = numeric(L)
Series=supervised[,1]

for(i in 1:L){
  X = e_garch[i]
  dim(X) = c(1,1,1)
  yhat = model.lstm %>% predict(X, batch_size=batch_size)
  # invert scaling
  yhat = reverse_scaling(yhat, scaler,  c(-1, 1))
  # invert differencing
  yhat  = yhat + as.numeric(Series[(n_+i)])
  # store
  predictions3[i] <- yhat
}
predictions3
```




```{r}
hybrid_garchlstm_pred<-predictions3+ garchMAE$x2

a<-test
hybrid_garchlstm_pred_mae<-mae(hybrid_garchlstm_pred, a[,2])
hybrid_garchlstm_pred_mse<-mse(hybrid_garchlstm_pred, a[,2])
hybrid_garchlstm_pred_rmse<-rmse(hybrid_garchlstm_pred, a[,2])
hybrid_garchlstm_pred_mape<-mape(hybrid_garchlstm_pred, a[,2])
GARCH_LSTM<-cbind(hybrid_garchlstm_pred_mae, hybrid_garchlstm_pred_mape, hybrid_garchlstm_pred_mse, hybrid_garchlstm_pred_rmse)

```






```{r}
ts.closed_nasdaq5<-ts(test[,2],frequency=365)
deneme9<-ts(hybrid_garchlstm_pred,frequency = 365)
df9<-as.data.frame(cbind(deneme9,ts.closed_nasdaq5))
df9$actual <- "actual"
df9$prediction<-"prediction"
satir9 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih9<- nasdaq5[(satir7+1):1206,]
df9%>%
  ggplot(aes(x=tarih9$nasdaq.Date..1.,y=deneme9,group=prediction,color=prediction))+
  geom_line(aes(y=ts.closed_nasdaq5,group=actual,color=actual))+
  geom_line(aes(y=deneme9,group=prediction,color=prediction))+
  labs(x = "Date", y = "NASDAQ Closed Value", color = "Data\n") +
  scale_color_manual(labels = c("Prediction", "Actual"), values = c("blue", "red")) 
  scale_y_continuous( limits=c(-0.04, 0.04))

```









#HATALARIN KARSILASTIRILMASI

```{r}
SONUC<-rbind(LSTMe,GARCHe,ARIMAe,SVMe,ARIMA_SVM,GARCH_SVM,GARCH_LSTM,ARIMA_LSTM)
row.names(SONUC) <-c("LSTM","ARIMA-EGARCH","ARIMA","SVM","ARIMA_SVM","ARIMA-EGARCH_SVM","ARIMA-EGARCH_LSTM","ARIMA_LSTM")
colnames(SONUC)<-c("MAE","MAPE","MSE","RMSE")
SONUC<-as.data.frame(SONUC)

min(SONUC$MAE)
```
```{r}
write.csv(SONUC, "NASDAQ_SONUC.csv", row.names = T)

```

```{r}
write.csv(hybrid_svmarima_pred,"pred_nasdaq.csv")
```

```{r}
write.csv(nasdaq3,"test.xlsx",row.names=T)

```

```{r}
hybrid_svmarima_pred
```


```{r}
forecast_garchsvm_nsq=nasdaq3 %>% slice(1207:1207)+hybrid_svmgarch_pred[362]

forecast_arimasvm_nsq=nasdaq3 %>% slice(1207:1207)+hybrid_svmarima_pred[362]
exp(forecast_arimasvm_nsq)
```

```{r}

```


```{r}
test3<-test[1]
test4<-test3[-c(362),]
test4[362] = 15474.22
as.data.frame(test4)
```
```{r}
yeni_test=nasdaq3 %>% tail(362)
yeni_test
test4<-yeni_test

```

```{r}
#RMSE PREDICTION DONUSTURULMUS HESAP

rmse_hesap<-read_xlsx("Yeni Microsoft Excel Çalışma Sayfası.xlsx")
rmse_nasdaq<-rmse(rmse_hesap$EXP,as.numeric(as.data.frame(nasdaq2[845:1207,])))
rmse_nasdaq
```

```{r}
write.csv(nasdaq2,"test2.csv")
```



```{r}
test4<-exp(test4)
test4<-test4%>%
  add_row(Close=15469.22)
test4<-test4[-c(362),]
ts.closed_nasdaq5<-ts(test4,frequency=365)
deneme7<-ts(hybrid_svmarima_pred+yeni_test,frequency = 365)
df7<-as.data.frame(cbind(deneme7,ts.closed_nasdaq5))
 df7$actual <- "actual"
df7$prediction<-"prediction"
satir7 <- round(nrow(nasdaq5) * .70, digits = 0)
tarih7<- nasdaq5[(satir7+1):1206,]
df7%>%
  ggplot(aes(x=tarih7$nasdaq.Date..1.,y=exp(deneme7),group=prediction,color=prediction))+
  geom_line(aes(y=ts.closed_nasdaq5,group=actual,color=actual))+
  geom_line(aes(y=exp(deneme7),group=prediction,color=prediction))+
  labs(x = "Date", y = "NASDAQ Closed Value", color = "Data\n") +
  scale_color_manual(labels = c("Prediction", "Actual"), values = c("blue", "red")) 

scale_y_continuous( limits=c(8750, 20000))
```


```{r}
Date=(1:724)
df_x<-as.data.frame(rbind(deneme7,ts.closed_nasdaq5))
df_x$set<-"prediction"
df_x$set[df_x$Close > 362] <- "actual"

ggplot(df7, aes(x=tarih7$nasdaq.Date..1., y=exp(deneme7), group=actual)) +
  geom_line(aes(shape=set, color=prediction))
```







grafikte gösterilecek


